### 2023-06-12 README.Rmd
Improved conditioning plot, and added option of interim saving of results following projections.

>>>>

* 2023-06-11 aMSE 0.1.5 Modified the condition plot and fixed up a few places where numbers were hard wired into the software. Introduced a new option to save output following projections (just in case of experiments with subsequent analyses crash - I'm looking at you SA). Now one can set interimout =c(outdir,postfixdir) and that should save a tempout into your outdir directory. See the help for do_MSE.

* 2023-06-04 aMSE 0.1.4 Small modifications to generalize across jurisdictions and allow for the consthcr constant catch harvest strategy; also removed irrelavent messages when plotting the phase plot

* 2023-06-03 aMSE 0.1.3 Modified to allow the mcdahcr and constrefhcr HCR to run successfully with the conditioned SA setup.
